Supplemental Materials, Methods and Results

### 2021-08-18 supp.Rmd
Added new Table style. INteraction models are provided in new supplementary table

>>>>

```{r tableS9, tab.cap = "Estimated model parameters, standard errors (SE), degrees of freedom (df) along with 95% confidence interval for each parameter. Full interaction models are presented for chromatic and luminance change (absolute JND)."}
tab9 <- read.csv("./output/tables/Table5_MS.csv")

Table9 <- flextable(tab9) %>% table_style13() %>% fit_to_width(max_width = 7)
Table9
```
